---
title: '`r res$search`'
author: "J Bhasin"
date: '`r Sys.Date()`'
output:
  html_document:
    toc: yes
---

```{r setup, include=FALSE}
library(data.table)
library(ggplot2)
library(handy)
library(knitr)
library(gtools)
library(stringr)
knitr::opts_chunk$set(cache=FALSE)
knitr::opts_chunk$set(eval=TRUE)
knitr::opts_chunk$set(include=FALSE)
knitr::opts_chunk$set(warning=FALSE)
knitr::opts_chunk$set(echo=FALSE)
```

# Trends

## By Year

```{r plot-year,include=TRUE}
ggplot(res$year,aes(x=year,y=papers)) + geom_point() + geom_line() + ggnice()
```

## By Institution

```{r kable-inst,include=TRUE}
res$aff <- data.table(res$aff)
kable(head(res$aff,15),format.args = list(big.mark = ","))
```

## By Country

```{r kable-count,include=TRUE}
res$country <- data.table(res$country)
kable(head(res$country,15),format.args = list(big.mark = ","))
```

## By Journal

```{r plot-journal,include=TRUE}
dt <- data.table(res$journal)
dt <- head(dt,15)
dt$journal <- factor(dt$journal,levels=rev(dt$journal))
ggplot(dt,aes(x=journal,y=papers)) + geom_bar(stat="identity") + coord_flip() + ggnice()
```

## By Grants

Click grant ID to search on Grantome.org

```{r kable-grants,include=TRUE}
dt <- data.table(res$grants)

dt$name <- paste0("<a href=\"http://grantome.com/search?q=",dt$name,"\">",dt$name,"</a>")

kable(head(dt,15),format.args = list(big.mark = ","))
```

## By Citation Count (in PMC)

### Citation Distribution

```{r plot-cites,include=TRUE}
ggplot(res$citation,aes(x=pmc_cites)) + geom_histogram(binwidth=10) + ggnice()
```

### Most Cited Papers

Click PMID to view PubMed record

```{r kable-cited,include=TRUE}
dt <- res$citation
dt$pmid <- paste0("<a href=\"http://www.ncbi.nlm.nih.gov/pubmed/",dt$pmid,"\">",dt$pmid,"</a>")
kable(head(dt,15))
```

# Authorship Network

## By Authors

### All Authors
```{r plot-aut-all,include=TRUE}
dt <- data.table(res$authors)
dt <- head(dt,20)
dt$papers <- as.integer(dt$papers)
dt$name <- factor(dt$name,levels=rev(dt$name))
ggplot(dt,aes(x=name,y=papers)) + geom_bar(stat="identity") + coord_flip() + ggnice()
```

### First Authors
```{r plot-aut-first,include=TRUE}
dt <- data.table(res$authors_first)
dt <- head(dt,20)
dt$papers <- as.integer(dt$papers)
dt$name <- factor(dt$name,levels=rev(dt$name))
ggplot(dt,aes(x=name,y=papers)) + geom_bar(stat="identity") + coord_flip() + ggnice()
```

### Last Authors
```{r plot-aut-last,include=TRUE}
dt <- data.table(res$authors_last)
dt <- head(dt,20)
dt$name <- factor(dt$name,levels=rev(dt$name))
dt$papers <- as.integer(dt$papers)
ggplot(dt,aes(x=name,y=papers)) + geom_bar(stat="identity") + coord_flip() + ggnice()
```

### Author Pairs

```{r kable-aut-pairs,include=TRUE}
dt <- res$author_pairs
kable(head(dt,15))
```

### Author Trios

```{r kable-aut-trios,include=TRUE}
dt <- res$author_trios
kable(head(dt,15))
```

### Author Network
```{r aut-net,include=TRUE}
# Build edgelist and nodelist
library(igraph)
nl <- data.table(res$authors)
el <- res$author_pairs
ig <- graph.data.frame(el, directed=FALSE)
#ig <- delete_vertices(ig,10:length(degree(ig)))
#table((nl$name %in% el$V1)|(nl$name %in% el$V2))
#nl <- nl[papers>3,]
#nl <- head(nl,10)
#el <- el[(V1 %in% nl$name) & (V2 %in% nl$name),]
#niet <- network(el,directed=FALSE)

deg <- igraph::degree(ig, mode="all")
V(ig)$size <- log(deg)
V(ig)$label <- NA

# Set edge width based on weight:
E(ig)$width <- log(E(ig)$papers)

#plot(ig)

dt <- data.table(author=names(deg),degree=deg)
dt <- dt[order(dt$degree,decreasing=T),]
kable(head(dt,10))
```

# Content Summary

## By MESH Terms

```{r mesh,include=TRUE}
dt <- data.table(res$mesh)
dt <- dt[!(dt$mesh %in% c("Humans","Animals","Mice","Male","Female")),]

library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer) 
colors <- brewer.pal(8, "Dark2")
set.seed(1234)
wordcloud(dt$mesh,dt$Freq,max.words=50, random.order=FALSE, rot.per=0.25,use.r.layout=FALSE, colors=colors)

kable(head(dt,10))
```

## MESH Term Network
```{r mesh-pairs,include=TRUE}
ig <- graph.data.frame(res$mesh_pairs, directed=FALSE)
#ig <- delete_vertices(ig,10:length(degree(ig)))
#table((nl$name %in% el$V1)|(nl$name %in% el$V2))
#nl <- nl[papers>3,]
#nl <- head(nl,10)
#el <- el[(V1 %in% nl$name) & (V2 %in% nl$name),]
#niet <- network(el,directed=FALSE)

deg <- igraph::degree(ig, mode="all")
V(ig)$size <- log(deg)
V(ig)$label <- NA

# Set edge width based on weight:
#E(ig)$width <- log(E(ig)$papers)

#plot(ig)
```

### MESH Term Degrees

```{r mes-deg,include=TRUE}
dt <- data.table(term=names(deg),degree=deg)
dt <- dt[order(dt$degree,decreasing=T),]
kable(head(dt,10))
```

### MESH Pairs
```{r mesh-pairs-tab,include=TRUE}
kable(head(res$mesh_pairs,15))
```

## Abstract Wordcloud
```{r abs,include=TRUE}
dt <- data.table(res$abswc)
dt <- dt[!(dt$term %in% c("the","this","Humans","Animals","Mice","Male","Female")),]

set.seed(1234)
wordcloud(dt$term,dt$n,max.words=50, random.order=FALSE, rot.per=0.25,use.r.layout=FALSE, colors=colors)

kable(head(dt,10))
```

